The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-28 manuscript/manuscript.Rnw
add missing significant
the top 1% and top 100 are by FPKM

Supplemental \cref{fig:transcriptome_statistics} shows the RNAseq read and
alignment statistics for all species. For transcriptomes sequenced
with 76 bp %
%
(\Sexpr{species(star.logs.wide[input.read.length > 70 & input.read.length < 80,unique(species)])}),%
%
the number of trimmed reads ranged from %
\Sexpr{star.logs.wide[input.read.length > 70 & input.read.length < 80,min(as.numeric(input.reads))]} 
%
to %
\Sexpr{star.logs.wide[input.read.length > 70 & input.read.length < 80,max(as.numeric(input.reads))]}
with an average of \Sexpr{star.logs.wide[input.read.length > 70 & input.read.length < 80,mean(`% good reads`)]}\% of reads 
mapping to the respective reference genome (\cref{tab:ref_genome_aligned_species}). 
%
For transcriptomes sequenced with 150 bp %
% The mismatch here is because we're reporting trimmed reads here, not
% full length reads
(\Sexpr{species(star.logs.wide[input.read.length > 120 & input.read.length < 160,unique(species)])}),
%
the number of trimmed reads ranged from %
\Sexpr{star.logs.wide[input.read.length > 120 & input.read.length < 160,min(as.numeric(input.reads))]} 
%
to %
\Sexpr{star.logs.wide[input.read.length  > 120 & input.read.length < 160,max(as.numeric(input.reads))]}
%
with an average of \Sexpr{star.logs.wide[input.read.length > 120 & input.read.length < 160,mean(`% good reads`)]}\% %
of reads mapping to the
respective reference genome (Supplemental \cref{tab:ref_genome_aligned_species}).
%
%
For transcriptomes sequenced with 100 bp %
% The mismatch here is because we're reporting trimmed reads here, not
% full length reads
(\Sexpr{species(star.logs.wide[input.read.length > 80 & input.read.length < 120,unique(species)])}),
%
the number of trimmed reads ranged from %
\Sexpr{star.logs.wide[input.read.length > 80 & input.read.length < 120,min(as.numeric(input.reads))]} 
%
to %
\Sexpr{star.logs.wide[input.read.length  > 80 & input.read.length < 120,max(as.numeric(input.reads))]}
%
with an average of \Sexpr{star.logs.wide[input.read.length > 80 & input.read.length < 120,mean(`% good reads`)]}\% %
of reads mapping to the
respective reference genome (Supplemental \cref{tab:ref_genome_aligned_species}).
%
%
For transcriptomes sequenced with 35 bp %
% The mismatch here is because we're reporting trimmed reads here, not
% full length reads
(\Sexpr{species(star.logs.wide[input.read.length < 40 ,unique(species)])}),
%
the number of trimmed reads ranged from %
\Sexpr{star.logs.wide[input.read.length < 40 ,min(as.numeric(input.reads))]} 
%
to %
\Sexpr{star.logs.wide[input.read.length  < 40  ,max(as.numeric(input.reads))]}
%
with an average of %
\Sexpr{star.logs.wide[input.read.length < 40, mean(`% good reads`)]}\%
%
of reads mapping to the respective reference genome (Supplemental
\cref{tab:ref_genome_aligned_species}). Read length was not a
predictor of unmapped read percentage (Supplemental
\cref{fig:transcriptome_reads_vs_read_length}). The expression of
all genes with \ac{FPKM} $\ge 50$ is shown in Supplemental
\cref{tab:all_ateles_fusciceps_placenta,tab:all_homo_sapiens_placenta,tab:all_pan_paniscus_placenta,tab:all_mus_musculus_placenta,tab:all_spalax_galili_placenta,tab:all_spalax_carmeli_placenta,tab:all_bos_taurus_placenta,tab:all_ovis_aries_placenta,tab:all_sus_scrofa_placenta,tab:all_equus_caballus_placenta,tab:all_canis_familiaris_placenta,tab:all_loxodonta_africana_placenta,tab:all_dasypus_novemcinctus_placenta,tab:all_monodelphis_domestica_placenta}.

@@

We performed \ac{gsea} on both the top 1\% of transcripts
(Supplemental \cref{tab:go_terms_enriched_top_one_ateles_fusciceps,tab:go_terms_enriched_top_one_homo_sapiens,tab:go_terms_enriched_top_one_pan_paniscus,tab:go_terms_enriched_top_one_mus_musculus,tab:go_terms_enriched_top_one_spalax_galili,tab:go_terms_enriched_top_one_spalax_carmeli,tab:go_terms_enriched_top_one_bos_taurus,tab:go_terms_enriched_top_one_ovis_aries,tab:go_terms_enriched_top_one_sus_scrofa,tab:go_terms_enriched_top_one_equus_caballus,tab:go_terms_enriched_top_one_canis_familiaris,tab:go_terms_enriched_top_one_loxodonta_africana,tab:go_terms_enriched_top_one_dasypus_novemcinctus,tab:go_terms_enriched_top_one_monodelphis_domestica}) and the top
100 transcripts (Supplemental
\cref{tab:go_terms_enriched_ateles_fusciceps,tab:go_terms_enriched_homo_sapiens,tab:go_terms_enriched_pan_paniscus,tab:go_terms_enriched_mus_musculus,tab:go_terms_enriched_spalax_galili,tab:go_terms_enriched_spalax_carmeli,tab:go_terms_enriched_bos_taurus,tab:go_terms_enriched_ovis_aries,tab:go_terms_enriched_sus_scrofa,tab:go_terms_enriched_equus_caballus,tab:go_terms_enriched_canis_familiaris,tab:go_terms_enriched_loxodonta_africana,tab:go_terms_enriched_dasypus_novemcinctus,tab:go_terms_enriched_monodelphis_domestica}); common processes
include protein transport and viral transcription/expression
(Supplemental \cref{tab:go_terms_all_species}).

>>>>

Supplemental \cref{fig:transcriptome_statistics} shows the RNAseq read and
alignment statistics for all species. For transcriptomes sequenced
with 76 bp %
%
(\Sexpr{species(star.logs.wide[input.read.length > 70 & input.read.length < 80,unique(species)])}),%
%
the number of trimmed reads ranged from %
\Sexpr{star.logs.wide[input.read.length > 70 & input.read.length < 80,min(as.numeric(input.reads))]} 
%
to %
\Sexpr{star.logs.wide[input.read.length > 70 & input.read.length < 80,max(as.numeric(input.reads))]}
with an average of \Sexpr{star.logs.wide[input.read.length > 70 & input.read.length < 80,mean(`% good reads`)]}\% of reads 
mapping to the respective reference genome (\cref{tab:ref_genome_aligned_species}). 
%
For transcriptomes sequenced with 150 bp %
% The mismatch here is because we're reporting trimmed reads here, not
% full length reads
(\Sexpr{species(star.logs.wide[input.read.length > 120 & input.read.length < 160,unique(species)])}),
%
the number of trimmed reads ranged from %
\Sexpr{star.logs.wide[input.read.length > 120 & input.read.length < 160,min(as.numeric(input.reads))]} 
%
to %
\Sexpr{star.logs.wide[input.read.length  > 120 & input.read.length < 160,max(as.numeric(input.reads))]}
%
with an average of \Sexpr{star.logs.wide[input.read.length > 120 & input.read.length < 160,mean(`% good reads`)]}\% %
of reads mapping to the
respective reference genome (Supplemental \cref{tab:ref_genome_aligned_species}).
%
%
For transcriptomes sequenced with 100 bp %
% The mismatch here is because we're reporting trimmed reads here, not
% full length reads
(\Sexpr{species(star.logs.wide[input.read.length > 80 & input.read.length < 120,unique(species)])}),
%
the number of trimmed reads ranged from %
\Sexpr{star.logs.wide[input.read.length > 80 & input.read.length < 120,min(as.numeric(input.reads))]} 
%
to %
\Sexpr{star.logs.wide[input.read.length  > 80 & input.read.length < 120,max(as.numeric(input.reads))]}
%
with an average of \Sexpr{star.logs.wide[input.read.length > 80 & input.read.length < 120,mean(`% good reads`)]}\% %
of reads mapping to the
respective reference genome (Supplemental \cref{tab:ref_genome_aligned_species}).
%
%
For transcriptomes sequenced with 35 bp %
% The mismatch here is because we're reporting trimmed reads here, not
% full length reads
(\Sexpr{species(star.logs.wide[input.read.length < 40 ,unique(species)])}),
%
the number of trimmed reads ranged from %
\Sexpr{star.logs.wide[input.read.length < 40 ,min(as.numeric(input.reads))]} 
%
to %
\Sexpr{star.logs.wide[input.read.length  < 40  ,max(as.numeric(input.reads))]}
%
with an average of %
\Sexpr{star.logs.wide[input.read.length < 40, mean(`% good reads`)]}\%
%
of reads mapping to the respective reference genome (Supplemental
\cref{tab:ref_genome_aligned_species}). Read length was not a
significant predictor of unmapped read percentage (Supplemental
\cref{fig:transcriptome_reads_vs_read_length}). The expression of
all genes with \ac{FPKM} $\ge 50$ is shown in Supplemental
\cref{tab:all_ateles_fusciceps_placenta,tab:all_homo_sapiens_placenta,tab:all_pan_paniscus_placenta,tab:all_mus_musculus_placenta,tab:all_spalax_galili_placenta,tab:all_spalax_carmeli_placenta,tab:all_bos_taurus_placenta,tab:all_ovis_aries_placenta,tab:all_sus_scrofa_placenta,tab:all_equus_caballus_placenta,tab:all_canis_familiaris_placenta,tab:all_loxodonta_africana_placenta,tab:all_dasypus_novemcinctus_placenta,tab:all_monodelphis_domestica_placenta}.

@@

We performed \ac{gsea} on both the top 1\% of transcripts by \ac{FPKM}
(Supplemental \cref{tab:go_terms_enriched_top_one_ateles_fusciceps,tab:go_terms_enriched_top_one_homo_sapiens,tab:go_terms_enriched_top_one_pan_paniscus,tab:go_terms_enriched_top_one_mus_musculus,tab:go_terms_enriched_top_one_spalax_galili,tab:go_terms_enriched_top_one_spalax_carmeli,tab:go_terms_enriched_top_one_bos_taurus,tab:go_terms_enriched_top_one_ovis_aries,tab:go_terms_enriched_top_one_sus_scrofa,tab:go_terms_enriched_top_one_equus_caballus,tab:go_terms_enriched_top_one_canis_familiaris,tab:go_terms_enriched_top_one_loxodonta_africana,tab:go_terms_enriched_top_one_dasypus_novemcinctus,tab:go_terms_enriched_top_one_monodelphis_domestica}) and the top
100 transcripts by \ac{FPKM} (Supplemental
\cref{tab:go_terms_enriched_ateles_fusciceps,tab:go_terms_enriched_homo_sapiens,tab:go_terms_enriched_pan_paniscus,tab:go_terms_enriched_mus_musculus,tab:go_terms_enriched_spalax_galili,tab:go_terms_enriched_spalax_carmeli,tab:go_terms_enriched_bos_taurus,tab:go_terms_enriched_ovis_aries,tab:go_terms_enriched_sus_scrofa,tab:go_terms_enriched_equus_caballus,tab:go_terms_enriched_canis_familiaris,tab:go_terms_enriched_loxodonta_africana,tab:go_terms_enriched_dasypus_novemcinctus,tab:go_terms_enriched_monodelphis_domestica}); common processes
include protein transport and viral transcription/expression
(Supplemental \cref{tab:go_terms_all_species}).
